A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using SVD or HOSVD: Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation

### 2018-12-02 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018.tex
Completed the new section on latest development in SVD aka 'PCA,SVD,KLT and Reservoir Characterisation'; Also updated references

Several studies were carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, King1996, Indelman_1993, Vereecken_2007, Wen_1996, Yeo2001}. \citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for oil reservoirs with varying permeabilities. The general conclusion reached from this study was that the equivalent permeability lies between the harmonic and the arithmetic average.

@@

>>>>

Several studies were carried out on the upscaling of permeability fields \cite{Christie_2001SPE10Model, Ewing_1997, Hasting_2001, Indelman_1993, King1996, Vereecken_2007, Wen_1996, Yeo2001}. \citet{Cardwell_1945} investigated arithmetic and weighted averages as upscaling techniques for calculating a single equivalent permeability for oil reservoirs with varying permeabilities. The general conclusion reached from this study was that the equivalent permeability lies between the harmonic and the arithmetic average.

@@

\subsection{PCA, SVD, POD, KLT and Reservoir Characterisation}\label{section:reservoir_char}

PCA, SVD and POD are closely related. In the petroleum engineering community where these techniques are used for reservoir characterization, they are sometimes used interchangable, and are normally referred to as the Karhunen-Loeve Transformation (KLT) \cite{Jafarpour_2009}.

A lot of the recent research in the field of petroleum engineering field which use these techniques, focus on the problem of history matching \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}. History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces the past behaviour (flow rate, production volume or pressures) of a reservoir, and hopefully predict its future behaviour as well \cite{Rwechungura_2011}. It is important to note that the model(s) referred to here could be a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.

\citet{Jafarpour_2009} compares KLT to discrete cosine transform (DCT) and goes on to state that the DCT is computationally more efficient than the KLT while being almost as accurate. \citet{Tavakoli_2010} noted that history matching calculation of sensitivities for all production data with respect to system parameters (\ie{variables}) is not feasible. Hence, they (\citet{Tavakoli_2010}) explored a new parameterization for reducing the number of variables based on the principal right singular vectors of the dimensionless sensitivity matix.

Perhaps, the works of \citet{Afra_2013}, \citet{Afra_2016}, \citet{Afra_2014}, \citet{Insuasty_2017} are more closely related to the one performed here. However, similar to the work of \citet{Jafarpour_2009}, they are more related to comparing several realizations than reducing the dimensionality of the dataset for a single realization. The work of \citet{Xiao_2018} is also closely related to that performed here and interestingly, they used the same CVFEM simulator used in this work. However, like the work of \citet{Tavakoli_2010}, the \citeauthor{Xiao_2018} were more interested in reducing the number of variable used to describe the system.

Essentially, the recent developments in the field of petroleum engineering described here make use of SVD to select the most suitable realization from multiple realizations or to reduce the representative system variables. However, the work described here is concerned with reducing dimensionality of the dataset for a single realization of one of the system variable (\ie{permeability}).
